\subsection{Implementation}
First we decided to work everyday at the university so as to make communication between members of the group easier.
Allowing us to solve bug faster, avoid derivation from the specification and cut the wok dynamically(reevaluate 
planning in real time when need be).\\
For each step, before beginning anything, we would all read and understand the subject. Then discuss with each other,
establish a "todo list" and then we would distribute the work.\\ 
Then, during the implementation, we would often make summary of our work to explain the implementation of every part 
of the code to the rest of the group.\\
To make the group work easier we used a git repository. This allowed us to share our work more efficiently as code
this tool can manage code merges automatically or at least make them easier. And allow us to work even when not
at the university and still be able to share the code immediately if need be.\\

\subsection{Validation}
Following the principle of the test driven development a large set of automated regression tests were developed. 
It was used to validate the code or point out one or multiple bug / regressions in it in a comfortable, fast
way and easily understandable way. \\
A failure on a test will indicate what the test was about, thus allowing us to point out the error easily.And by 
doing the test before or during the implementation this automated tests can allow to easily monitor the state and the
advancement of the part currently being implemented.\\ Indeed During the beginning of the  implementation, one of 
the members would implement the tests while the other began coding which allows to have tests ready as soon as the 
program compiles. \\
Valgrind has also been extensively used to remove memory leaks and unsafe memory access. Thus suppressing a 
significant number of possible bugs in the program. The program should now be free of any illegal memory access
and memory leak.

\subsection{Part 1 to 4}

For the parts 1 to 4, we followed the subject and all worked on the same part. We usually split into two teams.
Splitting the works of the whole step into two main parts. In this teams, we practiced extreme programing so as to
compensate for the fact that all the work could not easily be split between each member. Thus making the debugging phase faster. During the complicated phases,
having two persons working on the same problem often allowed us to solve it faster and to avoid many bugs in the code
that a single person would not notice while coding.\\
Also, when working in pair (or triple) the tests were not done by the person who was currently coding, thus they 
were not made with the weakness of the program in mind and tested uniformly the program without sparing some part 
or another.

\subsection{Part 5 and 6}

The parts 5 and 6 were done in parallel. The group was separated in two teams, each team working on one step.
For the rest, the same philosophy as for the first parts was applied. That is, each team worked following the
extreme programing principle.\\
The git repository was split in two working branches to make the work easier for both team as the two part were
independent but required to work in the same files thus causing unnecessary conflicts and possibly bugs that would
disturb the team not causing them. We used tags to separate these two branches.

\subsection{Last two days}

On the last days, one person took care of the merging of the two branches. The other made a "todo List" for the report 
and presentation, then everyone took one part of it to prepare. 
